### 2013-06-11 Tex/chapters/model.tex
Text

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection. %[vgl. Grafik (villeicht)]
    The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]
    \\

>>>>

\subsection{Critical Temperature $T_c$ and Critical Exponents}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    %[vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents. The critical exponents should not be influenced by the
    disturbance paramter \(\sigma\) [citation needed]. So they will be
    used for consistency cross checking and comparision with the known
    exact values \cite[S. 59]{Pelissetto2002}.\\
    %~ [theorie mit dem Collaps]
    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection.
    In figure \ref{fig:binder_fit_s_0} such a fit is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
    is in very good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
    \begin{figure}[htbp]
        \centering
        \subfigure{\includegraphics[width=0.5\textwidth]{images/binder_fit_s_0}}
        \caption[Binder cumulant fitted with polynom of degree 4]
                {Binder cumulant fitted with polynom of degree 4
                (the errorbars are too small to see)}
        \label{fig:binder_fit_s_0}
    \end{figure}%[vgl. Grafik (villeicht)]
    % The arithmetic average of the intersections are plotted [hier schon?]
    %~ [Und den rest der Auswertung]
